
% -------------------------
% Resume in Latex
% ------------------------

\documentclass[letterpaper,12pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
% \usepackage[pdftex]{hyperref}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage[document]{ragged2e}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% -------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
\item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
  \newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\justify\begin{itemize}}
  \newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

% -------------------------------------------
%%%%%% CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

% ----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{{\Large Chad A. Toups}} & Email : \href{mailto:chad.toups@gmail.com}{chad.toups@gmail.com}\\
                                                                                 & Mobile : +1(225)485-5118 \\
\end{tabular*}


% -----------EXPERIENCE-----------------
\section{Experience} 
\resumeSubHeadingListStart

  \resumeSubheading
  {Foster the Code}{New Orleans, LA}
  {Scrum Master}{Oct 2017 - Present}
  \resumeItemListStart
    \resumeItem{Gym software}
    {Our Team built software solution for the Client to supply tailored 
    workout plans to their customers and a system to track their progress. 

      \begin{itemize}
        \item Facilitated Scrum Ceremonies
        \item Support the Product Owner and Dev Team
        \item Skilled up Dev Team with a better understanding of agile framework
        \item Kept up to date, prioritized, and groomed Backlog
        \item Facilitated better client - product owner relationship 
      \end{itemize}
    
    }
  \resumeItemListEnd

  \resumeItemListStart
    \resumeItem{Agile Curriculm}
    {The Client desired to layout course work and class requirements needed 
    to complete Secondary Education in an Agile inspired framework as well 
    as skills to better equip the student in making the transition into the 
    workforce and adulthood. 

      \begin{itemize}
        \item Held Scrum Events and Ceremonies 
        \item Planned and tracked the workflow in Trello
        \item Improved the learning experience by providing clear metrics 
        \item Limited work in progress 
        \item Built a schedule and curriculum for the client
        \item Leveraged  and taught Kanban best practices

      \end{itemize}

    }
    

  \resumeItemListEnd
\resumeSubHeadingListEnd

\resumeSubHeadingListStart

\resumeSubheading
  {Larry Laurence Construction Company (LLCC)}{New Orleans, LA}
  {Scrum Master}{Oct 2015 - Oct 2018}
  \resumeItemListStart
    \resumeItem{Construction Managment}
    {The Client desired the tools to organize, plan, and track progress 
    throughout projects. We established a useable definition of “done”, workflow, 
    approximate timelines, identified and removed blockers
    and outlined an estimated costs.

      \begin{itemize}
        \item Applied some Scrum processes
        \item Leveraged some Kanban methodology
        \item We layed out a workflow and schedule
        \item Normalized interoffice communication
      \end{itemize}

    }
    

  \resumeItemListEnd
\resumeSubHeadingListEnd

  % --------PROGRAMMING SKILLS------------
  \section{Skills}
  \resumeSubHeadingListStart
    \item{
      \textbf{Technologies}{: Github, Trello, MS Office, Wrike, JIRA, etc.}
      \hfill
      \textbf{Tools}{: git, \LaTeX, brew, bash, etc.}
    }
  \resumeSubHeadingListEnd

  % -----------EDUCATION-----------------
  \section{Education}
  \resumeSubHeadingListStart
  \resumeSubheading
  {Loyola University of New Orleans}{New Orleans, LA}
  {Bachelors of Business Administration;  GPA: 3.5}{Grad. May 2010}
  \resumeSubHeadingListEnd

  % ------------References----------------
  \section{References}
  Available upon request.

  % -------------------------------------------
\end{document}
